Reproduction

### 2024-12-03 pages/paper_evaluation.qmd
docs(quarto): address TODO and tweak 94% to 94.1%

<!-- TODO: Once complete, carefully go over again and check everything is correct -->

@@

  Parameters:
  -----------
  df : pandas dataframe
    Dataframe with counts of fully, partially, not met and na items
  '''
  # Add reproduction success
  df['reproduce'] = [94, 37.5, 100, 100, 100, 80, 12.5, 100]

>>>>

@@

  Parameters:
  -----------
  df : pandas dataframe
    Dataframe with counts of fully, partially, not met and na items
  '''
  # Add reproduction success
  df['reproduce'] = [94.1, 37.5, 100, 100, 100, 80, 12.5, 100]

### 2024-12-03 pages/reproduction.qmd
feat(reproduction): add pale grid lines
docs(quarto): address TODO and tweak 94% to 94.1%

| Study | Scope | Success | Time |
| --- | --- | --- | --- |
| Shoaib and Ramamohan 2022 | 17 items:<br>• 1 table<br>• 9 figures<br>• 7 in-text results | 16 out of 17 (94%) | 28h 14m |
| Huang et al. 2019 | 8 items:<br>• 5 figures<br>• 3 in-text results | 3 out of 8 (37.5%) | 24h 10m |
| Lim et al. 2020 | 9 items:<br>• 5 tables<br>• 4 figures | 9 out of 9 (100%) | 12h 27m |
| Kim et al. 2021 | 10 items:<br>• 3 tables<br>• 6 figures<br>• 1 in-text result | 10 out of 10 (100%) | 14h 42m |
| Anagnostou et al. 2022 | 1 item:<br>• 1 figure | 1 out of 1 (100%) | 2h 11m |
| Johnson et al. 2021 | 5 items:<br>• 1 table<br>• 4 figures | 4 out of 5 (80%) | 19h 49m |
| Hernandez et al. 2015 | 8 items:<br>• 6 figures<br>• 2 tables | 1 out of 8 (12.5%) | 17h 56m |
| Wood et al. 2021 | 5 items:<br>• 4 figures<br>• 1 table | 5 out of 5 (100%) | 3h 50m |

@@

# Create list with the dataframes, labels and colours, to use for each plot
# Include alternative label for article with % reproduced and time
# (rather than names), and a linestyle
to_plot = [
    (
        df_ana,
        'Anagnostou<br>et al. 2022',
        '#882255',
        '100% (1/1), 2h 11m',
        (0, (1, 1))
    ),
    (
        df_woo,
        'Wood et al.<br>2021',
        '#117733',
        '100% (5/5), 3h 50m',
        '--'
    ),
    (
        df_lim,
        'Lim et<br>al. 2020',
        '#4477aa',
        '100% (9/9), 12h 27m',
        '-.'
    ),
    (
        df_kim,
        'Kim et<br>al. 2021',
        '#ccbb44',
        '100% (10/10), 14h 42m',
        ':'
    ),
    (
        df_her,
        'Hernandez<br>et al. 2015',
        '#aa3377',
        '12.5% (1/8), 17h 56m',
        '-'
    ),
    (
        df_joh,
        'Johnson et<br>al. 2021',
        '#66ccee',
        '80% (4/5), 19h 49m',
        (0, (3, 1, 1, 1, 1, 1))
    ),
    (
        df_hua,
        'Huang et<br>al. 2019',
        '#228833',
        '37.5% (3/8), 24h 10m',
        (0, (3, 3, 1, 3, 1, 3))
    ),
    (
        df_sho,
        'Shoaib and<br>Ramamohan<br>2022',
        '#ee6677',
        '94% (16/17), 28h 14m',
        (5, (10, 3))
    )
]
```

@@

>>>>

| Study | Scope | Success | Time |
| --- | --- | --- | --- |
| Shoaib and Ramamohan 2022 | 17 items:<br>• 1 table<br>• 9 figures<br>• 7 in-text results | 16 out of 17 (94.1%) | 28h 14m |
| Huang et al. 2019 | 8 items:<br>• 5 figures<br>• 3 in-text results | 3 out of 8 (37.5%) | 24h 10m |
| Lim et al. 2020 | 9 items:<br>• 5 tables<br>• 4 figures | 9 out of 9 (100%) | 12h 27m |
| Kim et al. 2021 | 10 items:<br>• 3 tables<br>• 6 figures<br>• 1 in-text result | 10 out of 10 (100%) | 14h 42m |
| Anagnostou et al. 2022 | 1 item:<br>• 1 figure | 1 out of 1 (100%) | 2h 11m |
| Johnson et al. 2021 | 5 items:<br>• 1 table<br>• 4 figures | 4 out of 5 (80%) | 19h 49m |
| Hernandez et al. 2015 | 8 items:<br>• 6 figures<br>• 2 tables | 1 out of 8 (12.5%) | 17h 56m |
| Wood et al. 2021 | 5 items:<br>• 4 figures<br>• 1 table | 5 out of 5 (100%) | 3h 50m |

@@

# Create list with the dataframes, labels and colours, to use for each plot
# Include alternative label for article with % reproduced and time
# (rather than names), and a linestyle
to_plot = [
    (
        df_ana,
        'Anagnostou<br>et al. 2022',
        '#882255',
        '100% (1/1), 2h 11m',
        (0, (1, 1))
    ),
    (
        df_woo,
        'Wood et al.<br>2021',
        '#117733',
        '100% (5/5), 3h 50m',
        '--'
    ),
    (
        df_lim,
        'Lim et<br>al. 2020',
        '#4477aa',
        '100% (9/9), 12h 27m',
        '-.'
    ),
    (
        df_kim,
        'Kim et<br>al. 2021',
        '#ccbb44',
        '100% (10/10), 14h 42m',
        ':'
    ),
    (
        df_her,
        'Hernandez<br>et al. 2015',
        '#aa3377',
        '12.5% (1/8), 17h 56m',
        '-'
    ),
    (
        df_joh,
        'Johnson et<br>al. 2021',
        '#66ccee',
        '80% (4/5), 19h 49m',
        (0, (3, 1, 1, 1, 1, 1))
    ),
    (
        df_hua,
        'Huang et<br>al. 2019',
        '#228833',
        '37.5% (3/8), 24h 10m',
        (0, (3, 3, 1, 3, 1, 3))
    ),
    (
        df_sho,
        'Shoaib and<br>Ramamohan<br>2022',
        '#ee6677',
        '94.1% (16/17), 28h 14m',
        (5, (10, 3))
    )
]
```

@@

# Amend appearance
plt.xlim(0, 30)
plt.ylim(0, 100)
plt.xlabel('Time elapsed (hours)')
plt.ylabel('Percentage of items reproduced')
ax.yaxis.set_major_formatter(mtick.PercentFormatter())
ax.legend(loc='center left', bbox_to_anchor=(1, 0.5))
plt.grid(alpha=0.2)
